Data-Driven Hardware-in-the-Loop Plant Modeling for Self-Driving Vehicles

### 2022-10-05 paperIEEE-ROSE2022-Pres.tex
Uploaded presentation  paperIEEE-ROSE2022-Pres.tex

%==============================================================================
%     TITLE
%==============================================================================
\title[HIL Plant Modeling]{Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle}

\author[H.~Grady, N.~Nauman]{Hannah~Grady and Nicholas~Nauman 
\linebreak Advisor:~Dr.~Suruz~Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Bradley University] % (optional, but mostly needed)
{
  \inst{~}Department of Electrical and Computer Engineering\\
  Bradley University\\
  1501 W. Bradley Avenue\\
  Peoria, IL, 61625, USA
  \and
  \inst{~}\textbf{Sponsor:}~AutonomouStuff $|$~https://autonomoustuff.com/\\
  306 Erie Avenue, Morton, IL 61550\\
  Telephone:~309-291-0966, email:info.as.ap@hexagon.com
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[April~26,~2022]{Tuesday, April~26,~2022}

>>>>

%==============================================================================
%     TITLE
%==============================================================================
\title[HIL Plant Modeling]{Data-Driven Hardware-in-the-Loop Plant Modeling for Self-Driving Vehicles}

\author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman \and Md Suruz~Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Bradley University] % (optional, but mostly needed)
{
  \inst{~}Department of Electrical and Computer Engineering\\
  Bradley University, Peoria, Illinois, 61625, USA
  \and
  \inst{~}\textbf{Sponsor:}~AutonomouStuff $|$~https://autonomoustuff.com/\\
  306 Erie Avenue, Morton, IL 61550\\
  Telephone:~309-291-0966, email:info.as.ap@hexagon.com
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.
%

\date[IEEE ROSE,~2022]{IEEE International Symposium on Robotics and Sensors Environments $|$ Nov. 14-15,~2022 $|$ Hybrid $|$ Khalifa University, Abu Dhabi UAE}
